---
title: "R_template"
output: html_document
date: "2026-02-23"
---

## Setup 
- Which packages need to be installed ie:
  - library(tidyverse)
  - library(dartRverse)  #we use version 1.2.2 for kioloa
- Data to be readin/included for testing etc:
  - use a data folder within your documents to store any data you want to use for testing/working through examples etc. - then you can read in using relative paths ie:
  - test1 <- read.csv("./data/file.csv")
  - 
- Any other additions - ie 3rd party binaries (co-ancestry etc.)
  - put those into a binary folder within you documents

```{r setup, include=FALSE}
# Include packages/setup here 
```

## Introduction
### Learning outcomes
- Outcomes for the tutorial/presentation
  - Takeaways for participants

# What is the goal of this session? What will participants learn?
### Pre-requisites
# What prior knowledge do they need?
- Any prior knowledge required - whether it be R packages/other languages (C++? example)

### Workflow
# What is the structure of the session?
- Rough flow of the session ie:
    1. Introduction to topic
      1.1 Rough overview for layman
      1.2 In depth overview for specific use/case
    2. Maybe introduction to dataset being used
      2.1 Anything interesting about dataset - high levels of inbreeding/genetic structure
    3. Data wrangling
      3.1 Reading in data - ie if special format (tsv,bed,fasta etc)
        3.1.1 Anything special to be done to read in
      3.2 Any processing needs to be done after read in - index bam files etc.
    4. Basic example
      4.1 Walkthrough - basic example - setup background etc.
      4.2 Workthrough example
      4.3 Pose questions for participants to do
    5. More advanced example
      5.1 Background
      5.2 Walkthrough
    6. Wrap up/conclusion
    7. More reading/references
    
### Additional reading
#Anything else you want to add?
- References etc maybe papers for the writers - Ching Ching and Ethan to read if need be.


## Topic
# Brief recap of the topic, relating back to the presentation.



## Worked Ex:
# Worked example that everyone steps through together - simple example applying the methods
- Provide outline of examples to be written up
    - Ie datasets required
    - How to read them in
    - How you want them presented
    - Code of analysis to be done on them etc. etc.
    - even potential output you would like to see - (also allows us to know if weve done smoething wrong)

```{r example_template01, include=FALSE}
# Include code for examples here (01)
```

```{r example_template02, include=FALSE}
# Include code for examples here (02)
```

```{r example_template03, include=FALSE}
# Include code for examples here (03 etc...)
```


## Exercises
#Exercises where they can use their own data or supplied data to try out what they have learnt in a new context.
- Exercises - fairly straightforward maybe just provide code to be inserted for writing up

-   dot points
-   for different steps


```{r exercises_template01, include=FALSE}
# Include code for exercises here 
```

```{r exercises_template02, include=FALSE}
# Include code for exercises here 
```

```{r exercises_template03, include=FALSE}
# Include code for exercises here 
```

## Winding up
### Discussion Time
- Brief recap of what has been learnt/ground that has been covered.
    - Provide new directions for further reading - (ie if you liked this how about?)


#Add some questions to help group discussion.
### Where have we come?


#Summarise what they should have learnt.
- Final complete summary of whats been learnt/taught over the course of the tutorial



